Seasonality in governing dynamics at submesoscales

### 2016-06-11 writeup/rocha_etal.tex
Fixes yet another typo

Recent interest in upper-ocean dynamics has focused on the strong seasonal
cycle of shallow baroclinic instabilities and their role in submesoscale roughly 1-100 km)
turbulence and mesoscale modulation \citep{sasaki_etal2014,qiu_etal2014,
callies_etal2015, thompson_etal2016,buckingham_etal2016}. Contemporary studies
have also suggested that inertia-gravity waves contribute significantly
to the near-surface variability at submesoscales \citep{richman_etal2012,
buhler_etal2014,rocha_etal2016}, but their seasonality has not been investigated.

>>>>

Recent interest in upper-ocean dynamics has focused on the strong seasonal
cycle of shallow baroclinic instabilities and their role in submesoscale (roughly 1-100 km)
turbulence and mesoscale modulation \citep{sasaki_etal2014,qiu_etal2014,
callies_etal2015, thompson_etal2016,buckingham_etal2016}. Contemporary studies
have also suggested that inertia-gravity waves contribute significantly
to the near-surface variability at submesoscales \citep{richman_etal2012,
buhler_etal2014,rocha_etal2016}, but their seasonality has not been investigated.
